\documentclass[phd]{abdnthesis}

%% For citations, I would recommend natbib for its                          
%% flexibility, particularly when named citation styles are used, but                
%% it also has useful features for plain and those of that ilk.                      
%% The natbib package gives you the following definitons                             
%% that extend the simple \cite:                                                     
%   \citet{key} ==>>                Jones et al. (1990)                              
%   \citet*{key} ==>>               Jones, Baker, and Smith (1990)                   
%   \citep{key} ==>>                (Jones et al., 1990)                             
%   \citep*{key} ==>>               (Jones, Baker, and Smith, 1990)                  
%   \citep[chap. 2]{key} ==>>       (Jones et al., 1990, chap. 2)                    
%   \citep[e.g.][]{key} ==>>        (e.g. Jones et al., 1990)                        
%   \citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., p. 32)                       
%   \citeauthor{key} ==>>           Jones et al.                                     
%   \citeauthor*{key} ==>>          Jones, Baker, and Smith                          
%   \citeyear{key} ==>>             1990                                             

\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{scrextend}
\usepackage{pdfpages}
\usepackage{float}
\setlength{\bibsep}{0pt}
\bibliographystyle{apalike}

\usepackage[T1]{fontenc}
\usepackage{makecell}

\title{Using Natural Language Processing for Automatic Generation of Animated Dialogue Scenes in Video Games}
\author{Mikolaj \ Panasiuk}
% IMO this is a bit silly, but some like to include these. To remove,
% delete this declaration and remove the option from the
% \documentclass definition above.
%\qualifications{PhD, Computer Science, University College London, 1997\\%            
%BEng (Hons.) Electrical and Electronic Engineering, The University of Wales, Swansea, 1992}
\school{Department of Computing Science}

%%%% In the final submission of a thesis, this should only be the year
%%%% of submission.  However, it is useful to use \date{\today} for drafts so that
%%%% they don't get mixed up.
    
\date{2017}
\newcommand \videoshost{LINK TO VIDEOS}

%% It is useful to split the document up as chapters and include
%% them.  LaTeX will sort out all the numbering and cross-referencing
%% for you --- if you run it enough times!

%% If you want to include only a couple of chapters then use the
%% \includeonly{} command with a list of the file/chapter names that
%% you wish to include.  NB, this must be in the preamble.

\includeonly{introduction,background,analysis,faq, design, requirements, testingperf, usermanual, maintenance, evaluation, results, otherappend, conclusions, discussion}

\def\sfthing#1#2{\def#1{\mbox{{\small\normalfont\sffamily #2}}}}

\sfthing{\PP}{P}
\sfthing{\FF}{F}

%% This will make sure that all cross-references are correct (including
%% references to those file not included) but will produce a dvi
%% file with only those files/chapters you specify included.

\begin{document}

%%%% Create the title page and standard declaration.

\maketitle
\makedeclaration

%%%% Then the abstract and acknowledgements

\begin{abstract}
  Modern video games (especially those of the RPG genre) can feature over a hundred hours of dialogue. During the dialogue scene, the characters are expected to behave naturally and use body language in a way that is natural and corresponds to what they are saying. Due to the sheer amount of dialogue animation needed it is impossible to manually animate all the scenes. Many solutions to automatic generation of those scenes have been tried (most of which are not available publicly and still require a fair amount of manual work) with mixed results.
  
  This project aimed to develop a tool capable of generating 3D animated dialogue scenes with virtually none manual labour required. This is achieved by using natural language processing to extract the mood of characters directly from script and using a database of pre-recorded motion capture animations to assemble a dialogue scene. The tool was also aimed to be cross-platform, easy and cost-efficient to use, as such a tool would be most useful for small teams and amateur developers.
  
  The tool was evaluated by a real audience whose task were to compare scenes from actual games with scenes generated by the developed software. The tool succeeded in creating rather convincing animation that was often described as more enjoyable or engaging than the animations from games; Unfortunately the generated scenes lacked realism and the NLP approach was not accurate enough when dealing with sarcasm or ambiguity. Because of those issues the project did not achieve a full success.
  
  The software itself would need some serious improvements before becoming commercially viable. It is however developed enough to prove the usefulness of NLP in game animation. This approach has potential to be incorporated into a larger animation generation framework (where many approaches can collaborate to create the most lifelike animations) and even to be extended into other areas such as robotics. 
\end{abstract}

\begin{acknowledgements}
  I would like to thank Professor Ehud Reiter for his invaluable guidance, supervision and patience. 

  Secondly, I would like to thank the Blender Foundation for providing free, open-source, modern 3D content creation tools for over 15 years and the Max Planck Institute for Biological Cybernetics for making the Emotional Body Motion Database available publicly.
  
  I would also like to thank the BioWare Montreal studio for their failure in developing \textit{Mass Effect: Andromeda}. The spectacular fiasco of this game has brought attention to the importance of automatically generated dialogue animation and has been an inspiration for this project. I myself will keep pretending that this game has never happened and I am still happily waiting for the continuation of my favourite series (the same way I am still waiting for a sequel to \textit{The Matrix}). The following blank-verse poem commemorates the achievements, the failure and the disbandment of the BioWare Montreal studio:
  
  \bigskip
  \noindent \textbf{BioWare Montreal}\newline
  It seems like we hardly knew you,\newline
  probably because you only existed for 9 years and were very small\newline
  The more surprising is the fact that\newline
  you have been put in charge of the most significant of BioWare's franchises\newline
  \newline
  Pity,\newline
  because you looked like a pretty cool place to work at\newline
  Even though Glassdoor reviewers complained that there are no windows at the office\newline
  and that they all feel like nocturnal creatures.\newline
  Montreal also seems like a good place to live I guess\newline
  despite all the snow in the winter and the roadwork in the summer\newline
  But how would I know, I have never been to Canada anyway\newline
  \newline
  You should have went gently into that good night\newline
  But you didn't\newline
  And now your game is a laughing stock for the entire gaming community\newline
  Press F to pay respects\newline
  F
  
  
  
  
\end{acknowledgements}


% Tables 
\tableofcontents
\listoffigures
\listoftables

% Body
\include{introduction}
\include{background}
\include{analysis}
\include{requirements}
\include{design}
\include{testingperf}
\include{evaluation}
\include{results}
\include{discussion}
\include{conclusions}

% Bib
\bibliography{mybib}

% Appendix
\appendix
\include{usermanual}
\include{maintenance}
\include{otherappend}

\end{document}
